Carbonate chemistry at Ny-Ålesund

### 2021-03-02 awipev-CO2.Rmd
added depth_discrete for plotting seafet pH

d <- d_all %>% 
  as_tsibble(index = datetime) %>% 
  dplyr::arrange(datetime) %>%
  tsibble::fill_gaps() %>%
  dplyr::mutate(year_month = format(datetime, '%Y-%m'),
                quarter = quarter(datetime)) %>%
#  dplyr::rename(pco2_contros = pco2_corr) %>% 
  replace(., is.na(.), NA) # replace NaN by NA everywhere

d_ts <- d %>%
  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_fb,
                pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
  #tidyr::pivot_longer(-datetime, values_to = "value")

#sal_fb
ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Salinity FerryBox",x="", y="Salinity") +
  Mytheme(size_labs = 8)
# ts_sal_py <- ggplotly(ts_sal,dynamicTicks = TRUE)
# filename.html <- paste0(path_fig, "ts_sal_py.html")
# saveWidget(ts_sal_py, filename.html, selfcontained = T, libdir = "lib")

@@

# SEAFET pH
ts_pH <- d_all %>%
  ggplot(aes(x = datetime, y = pHint_tot_sf_9m), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="In situ pH below 8 m (seaFET in blue, spectrophotometric pH in red))",x="", y=expression(paste(pH[T]))) +
  Mytheme(size_labs = 8)

>>>>

# d <- d_all %>% 
#   as_tsibble(index = datetime) %>% 
#   dplyr::arrange(datetime) %>%
#   tsibble::fill_gaps() %>%
#   dplyr::mutate(year_month = format(datetime, '%Y-%m'),
#                 quarter = quarter(datetime)) %>%
# #  dplyr::rename(pco2_contros = pco2_corr) %>% 
#   replace(., is.na(.), NA) # replace NaN by NA everywhere
# 
#  autoplot(vars(Close, log(Close)))
#  
#  
# d_ts <- d %>%
#   dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_fb,
#                 pressure_insitu_ctd, pHint_tot_sf, ph_s_sf_temp_insi, at_calc, at) #%>%
#   #tidyr::pivot_longer(-datetime, values_to = "value")

#sal_fb
ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Salinity FerryBox",x="", y="Salinity") +
  Mytheme(size_labs = 8)

@@

# SEAFET pH
d_pH <- d_all %>% 
  dplyr::select(datetime, pressure_insitu_ctd, pHint_tot_sf) %>% tidyr::pivot_longer(-datetime, values_to = "value")
ts_pH <- d_all %>%
  ggplot(na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pHint_tot_sf_9m), colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="In situ pH below 8 m (seaFET in blue, spectrophotometric pH in red))",x="", y=expression(paste(pH[T]))) +
  Mytheme(size_labs = 8)
